Figures

### 2020-03-25 figures/02_depth_model.Rmd
create variable importance plot

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
# setwd("figures")
source("../scripts/99_utils.R")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 6.5, fig.height = 4.5)
if(interactive()){
  setwd("figures")
}
source("../scripts/99_utils.R")
```

@@

```{r 02_depth_model_importance, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3.5, fig.width=8}
dt_fits <- readRDS("../data/01_depth_model/depth_fits.rds")

tidy_importance <- function(x){
  # x <- dt_fits[[2]]$fit$fit
  res <- ranger::importance(x) %>%
  data.frame() %>% cbind(row.names(.), .[,1]) %>%
  setNames(c("percent_inc_mse", "variable"))
  row.names(res) <- NULL
  res <- res[,c(2, 1)]
  res <- arrange(res, percent_inc_mse)
  # res$variable <- factor(res$variable, levels = res$variable)
  res <- mutate(res, variable = as.character(variable))
  res <- mutate(res, variable = case_when(
    stringr::str_detect(variable, "maxdepth") ~ "trig_depth", 
    TRUE ~ variable)
    )
  res
}

dt_imp <- lapply(2:4, function(i) tidy_importance(dt_fits[[i]]$fit$fit))
model_names <- c("true_proxy", 
                 "proxy_true", 
                 "proxy_proxy")
dt_imp <- bind_rows(lapply(1:3, function(i){
  mutate(dt_imp[[i]], model = model_names[i])
  }))
dt_imp$model <- factor(dt_imp$model, levels = model_names)

var_order <- 
  group_by(dt_imp, variable) %>% 
  summarize(max = max(percent_inc_mse)) %>%
  arrange(max) %>%
  pull(variable)
dt_imp$variable <- factor(dt_imp$variable, levels = var_order)

ggplot() + 
  geom_point(data = dt_imp, aes(percent_inc_mse, variable, color = model)) +   
  # geom_hline(linetype = 3, size = 1, colour = "gray", 
  #                yintercept = 1:nlevels(dt$variable)) + 
  theme(text = element_text(family="Times"),
        panel.background = element_blank(), panel.grid = element_blank(),
        panel.border = element_rect(fill = NA), # legend.position = "none", 
        axis.title.x = element_text(family="sans", face = "bold", 
        vjust = -0.5, size = 12), 
        axis.text = element_text(family="sans",size = 11, 
                                 color = "black")) + 
        ylab("") + xlab("Percent Increase in Mean Square Error")
```

### 2020-03-25 manuscript/figures.Rmd
create variable importance plot

>>>>

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```
